Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-31 paper/current/main.tex
small paragraph change, fig 4

Re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
Linguistic and historical ties are also important.
For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c).
Similarly, Algeria and Morocco are near the French cluster (Fig.~\ref{fig:projection}a).
Comparable structural patterns exist even within a single country.
For example, organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.

>>>>

By learning and leveraging the embedding space, these complex national and regional relationships can be quantified and visualized.  
For example, by re-projecting or \textit{zooming into} organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
Linguistic and historical ties are also important.
For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c).
Similarly, Algeria and Morocco are near the French cluster (Fig.~\ref{fig:projection}a).
Comparable structural patterns exist even within a single country.
For example, organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.
